---
title: "HAAS_IRT_REPORT"
output: github_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r}
library(mokken)
library(mirt)
packageVersion("mokken")
packageVersion("mirt")
```


```{r}
HAAS <- readRDS("HAAS.rds")
HAAS <- as.data.frame(HAAS)
df <- HAAS
head(df)
```

# Dimensionality

```{r}
aisp1 <- aisp(df, search = 'normal', lowerbound=seq(.3,.8,by=.05))
aisp1
aisp2 <- aisp(df, search = 'ga', lowerbound=seq(.3,.8,by=.05))
aisp2

```

# Scalability

```{r}
H <- coefH(df)
```

# Minsize

The parameter below will determine the minimum size of the "rest groups" for tests of monotonicity, order invariance, local independence, etc.

If it is too large, it will not allow the construction of at least 2 groups, compromising the methods. If it is too small, it generates less reliable statistics.

From attempts we arrived at the value of 40.
```{r}
minsize <- 40
```

# Monotonicity

```{r}
monotonicity_test <- check.monotonicity(df, minsize = minsize)
summary(monotonicity_test)
```

```{r}
plot(monotonicity_test)
```

# IIO

```{r}
check.iio.test <- check.iio(
  df, 
  method = "MIIO", 
  minsize = minsize, 
  verbose = FALSE, 
  item.selection = FALSE,
)
summary(check.iio.test)
```

```{r}
par(mfrow=c(2,3))
plot(check.iio.test)
```

# Local Independence

```{r}
IL <- check.ca(df, Windex=T, MINSIZE=minsize)
IL$InScale
summary(IL)
```

## Reliability

```{r}
check.reliability(
  df,
  MS = TRUE,
  alpha = TRUE,
  lambda.2 = TRUE,
  LCRC = TRUE
)
```

# Parametric Model

```{r}
fitGraded <- mirt(df, 1, itemtype = "graded", SE = FALSE, verbose = TRUE)
summary(fitGraded)
```

```{r}
theta <- fscores(fitGraded, full.scores.SE = TRUE)
empirical_rxx(theta)
```

## M2

```{r}
M2(fitGraded, type = "C2", calcNULL = FALSE)
```

## Itemfit

```{r}
itemfit(fitGraded, p.adjust = 'fdr')
```

## Item Parameters

```{r}
params <- coef(fitGraded, IRTpars = TRUE, simplify = TRUE)
round(params$items, 2)
```

## Empirical CCI

```{r}
CCI_empirica <- lapply(
  1:ncol(df), 
  function(x) itemfit(fitGraded, empirical.plot = x)
)
CCI_empirica
```

## Trace Plot

```{r}
plot(fitGraded, type = 'trace')
```

## Info Plot

```{r}
plot(fitGraded, type = "infoSE")
plot(fitGraded, type = 'infotrace')
```

# Citation

```{r}
citation('mokken')
citation('mirt')
```
